Building Markov State Models for Periodically Driven Non-Equilibrium Systems

### 2014-11-06 writedown/period.noneq.msm/paper.tex
add keywords, some revises from CS

\documentclass[aps, pre, preprint,unsortedaddress,a4paper,onecolumn]{revtex4}
% \documentclass[aps, pre, reprint,unsortedaddress,a4paper,twocolumn]{revtex4}
% \documentclass[acs, jctcce, a4paper,preprint,unsortedaddress,onecolumn]{revtex4-1}
% \documentclass[aps,pre,twocolumn,unsortedaddress]{revtex4-1}
% \documentclass[aps,jcp,groupedaddress,twocolumn,unsortedaddress]{revtex4}

@@

\title{Building Markov State Models for Periodically Driven Non-Equilibrium Systems}
\author{Han Wang}
\email{han.wang@fu-berlin.de}
\affiliation{CAEP Software Center for High Performance Numerical Simulation, Beijing, China}
\affiliation{Zuse Institute Berlin, Germany}
\author{Christof Sch\"utte}
\email{Christof.Schuette@fu-berlin.de}
\affiliation{Institute for Mathematics, Freie Universit\"at Berlin, Germany}
\affiliation{Zuse Institute Berlin, Germany}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Core Set identification}

@@

\subsection{Irreversibility of the periodical symmetrical dynamics}

@@

\section{The prove of identity $\hat P = \hat T\hat M^{-1}$}
\label{sec:app-ptm}
In this section we prove the identity  $\hat P = \hat T\hat M^{-1}$. Starting from the
result Eq.~\eqref{eq:appb-t},
\begin{align*}
  \hat T_{jk} &=
  \prob [\,h_{t+T}(C_k) < h_{t+T}(\cup_{l\neq k} C_l) \,\vert\, \hat X_t = j\,]\\
  &=
  \frac{\prob [\,h_{t+T}(C_k) < h_{t+T}(\cup_{l\neq k} C_l), \hat X_t = j\,] }{\prob(\hat X_t = j)}\\
  & =
  \sum_l \frac{\prob [\,h_{t+T}(C_k) < h_{t+T}(\cup_{l\neq k} C_l), \hat X_{t+T} = l, \hat X_t = j\,] }{\prob(\hat X_t = j)}\\
  & =
  \sum_l \prob [\,h_{t+T}(C_k) < h_{t+T}(\cup_{l\neq k} C_l)\vert \hat X_{t+T} = l, \hat X_t = j\,] \hat P_{jl}\\  
  & =
  \sum_l \prob [\,h_{t+T}(C_k) < h_{t+T}(\cup_{l\neq k} C_l)\vert \hat X_{t+T} = l\,] \hat P_{jl}\\
  &= 
  \sum_l  \hat P_{jl}\hat M_{lk}.
\end{align*}
This proves the identity $\hat P = \hat T\hat M^{-1}$.
Notice that in the fifth equation we assumes the Markovianity of the milestone process $\hat X_m$. In the sixth equation we use the result Eq.~\eqref{eq:appb-m}, and the time-homogeneity of the milestone process.

>>>>

\documentclass[aps, pre, preprint,unsortedaddress,a4paper,onecolumn,showkeys]{revtex4}
% \documentclass[aps, pre, reprint,unsortedaddress,a4paper,twocolumn]{revtex4}
% \documentclass[acs, jctcce, a4paper,preprint,unsortedaddress,onecolumn]{revtex4-1}
% \documentclass[aps,pre,twocolumn,unsortedaddress]{revtex4-1}
% \documentclass[aps,jcp,groupedaddress,twocolumn,unsortedaddress]{revtex4}

@@

\title{Building Markov State Models for Periodically Driven Non-Equilibrium Systems}
\author{Han Wang}
\email{han.wang@fu-berlin.de}
\affiliation{CAEP Software Center for High Performance Numerical Simulation, Beijing, China}
\affiliation{Zuse Institute Berlin (ZIB), Germany}
\author{Christof Sch\"utte}
\email{schuette@zib.de}
\affiliation{Institute for Mathematics, Freie Universit\"at Berlin, Germany}
\affiliation{Zuse Institute Berlin (ZIB), Germany}

@@

\keywords{Non-equilibrium, Markov states model, Alanine dipeptide, Electric field, Floquet theory}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Core set identification}

@@

\subsection{Irreversibility of the periodic time-symmetric dynamics}

@@

\section{Prove of the identity $\hat P = \hat T\hat M^{-1}$}
\label{sec:app-ptm}
In this section we prove the identity  $\hat P = \hat T\hat M^{-1}$. Starting from the
result Eq.~\eqref{eq:appb-t},
\begin{align*}
  \hat T_{jk} &=
  \prob [\,h_{t+T}(C_k) < h_{t+T}(\cup_{l\neq k} C_l) \,\vert\, \hat X_t = j\,]\\
  &=
  \frac{\prob [\,h_{t+T}(C_k) < h_{t+T}(\cup_{l\neq k} C_l), \hat X_t = j\,] }{\prob(\hat X_t = j)}\\
  & =
  \sum_l \frac{\prob [\,h_{t+T}(C_k) < h_{t+T}(\cup_{l\neq k} C_l), \hat X_{t+T} = l, \hat X_t = j\,] }{\prob(\hat X_t = j)}\\
  & =
  \sum_l \prob [\,h_{t+T}(C_k) < h_{t+T}(\cup_{l\neq k} C_l)\vert \hat X_{t+T} = l, \hat X_t = j\,] \hat P_{jl}\\  
  & =
  \sum_l \prob [\,h_{t+T}(C_k) < h_{t+T}(\cup_{l\neq k} C_l)\vert \hat X_{t+T} = l\,] \hat P_{jl}\\
  &= 
  \sum_l  \hat P_{jl}\hat M_{lk}.
\end{align*}
This proves the identity $\hat P = \hat T\hat M^{-1}$.
Notice that in the fifth equation we assumes the Markovianity of the milestone process $\hat X_m$. In the sixth equation we use the result Eq.~\eqref{eq:appb-m}, and the time-homogeneity of the milestone process.
